Verifying Demonstrations

### 2018-06-01 paper/conclusions.tex
detailed pass on the paper

We have introduced \PRIVO, a protocol for verifiably counting participants at protests. Despite the verification, the privacy of the
participants is preserved to the extent possible by their physical
presence at the protest. To achieve that, we adapted the Schnorr
protocol to develop distance-bounding anonymous credentials. Except for receipt
freeness, which we cannot guarantee if the adversary gets access to
Alice's device and secret PRF key after her participation has
been witnessed and before she had a chance to
delete it, \PRIVO
fulfills all verification and privacy properties we derived from those
of electronic voting complemented by the specific constraints on time
and location required for protests.

Of separate interest, we can now provide distance bounding for authenticating 
more general attributes than provided by previous \ac{DB} protocols.
All privacy-preserving \ac{DB} protocols have so far focused on identity-based 
authentication, but not authentication of general attributes, as is the case 
for anonymous credentials.
With our contribution, Alice can now prove more complex statements to Bob, \eg 
that she is older than 18 but younger than 40 without revealing her actual age,  
and at the same time Bob can be sure that Alice is not just relaying messages 
from her older sister Carol.

In general, none of the related works fulfills the eligibility
verifiability (one proof per person, temporal and spatial eligibility ---
\cref{%
  CountOnce,%
  TemporallyRelated,SpatiallyRelated,%
}).
To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people 
usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but 
not individual verifiability (\cref{IndividualVerif}).
If they would provide individual verifiability, they would likely violate the 
privacy requirements.

Finally, most of the current methods are estimates, with quite some
error margins. While \PRIVO is an actual count and not an estimate,
its accuracy for the total number of participants hinges on the
participants having the necessary equipment (a smartphone or similar
device), some sort of trustworthy credential, and the willingness to
run the protocol. Owing to the network effect, until used by most
participants, \PRIVO would result in a considerable
undercount. However, it presents a first step toward accurate
verifiable yet privacy-preserving crowd counting by showing how it can
be done in theory at least and in practice once some assumptions
concerning hardware and e-identities become more realistic. While the
the necessary technologies are not yet available in most authoritarian
regimes, some of them are in several democracies. We believe that it
is important to implement systems such as ours also there to support
the maintenance of democratic processes.

>>>>

In this paper, we have introduced \PRIVO, a privacy-preserving protocol for verifiably counting participants at protests. 
Despite the verification, the privacy of the participants is preserved to the extent possible by their physical presence at the protest. 
To achieve that, we adapted the Schnorr protocol to develop distance-bounding anonymous credentials. 
Except for receipt freeness, which we cannot guarantee if the adversary gets access to Alice's device and secret PRF key after her participation has been witnessed and before she had a chance to delete it, \PRIVO fulfills all verification and privacy properties we derived from those of electronic voting complemented by the specific constraints on time and location required for protests.

Of separate interest, we have also build distance-bounding protocols for authenticating more general attributes than provided by previous \ac{DB} ones.
All privacy-preserving \ac{DB} protocols have so far focused on identity-based authentication, but not authentication of general attributes, as is the case for anonymous credentials.
With our contribution, Alice can now prove more complex statements to Bob, (\eg  that she is older than 18 but younger than 40 without revealing her actual age) and at the same time Bob can be sure that Alice is not just relaying messages from her older sister Carol.

In general, none of the related works fulfills the eligibility
verifiability (one proof per person, temporal and spatial eligibility ---
\cref{%
  CountOnce,%
  TemporallyRelated,SpatiallyRelated,%
}).
To some extent, some techniques do fulfill designated event (\cref{DesignatedEvent}), since people usually use placards in the protests.
Also, some schemes provide universal verifiability (\cref{UniversalVerif}), but not individual verifiability (\cref{IndividualVerif}).
Moreover, if they would provide individual verifiability, they would likely violate the privacy requirements.

Finally, most of the current methods are estimates, with quite some error margins. 
While \PRIVO is an actual count and not an estimate, its accuracy for the total number of participants hinges on theparticipants having the necessary equipment (\ie, a smartphone or similar device), some sort of trustworthy credential, and the willingness to run the protocol. 
Owing to the network effect, until used by most participants, \PRIVO would result in a considerable undercount. 
However, it represents a first step toward accurate verifiable yet privacy-preserving crowd counting by showing how it can be done in theory at least and in practice once some assumptions concerning hardware and e-identities become more realistic. 
While the the necessary technologies are not yet available in most authoritarian regimes, some of them are in several democracies. We believe that it is important to implement systems such as ours also there to support the maintenance of democratic processes.
